% !TeX program = xelatex

\documentclass[12pt,a4paper]{article}
    
\usepackage{fontspec}  
\usepackage{xcolor}
\usepackage{geometry}
\geometry{margin=2.5cm}
 
\setmainfont{Noto Serif}
\setsansfont{Noto Sans} 
\setmonofont{Noto Sans Mono}  
 
\newfontfamily\arabicfont[Script=Arabic]{Noto Sans Arabic}
\newfontfamily\cjkfont{Noto Sans CJK SC}

\newcommand{\textarabic}[1]{{\arabicfont\textdir TRT #1}}
\newcommand{\textcjk}[1]{{\cjkfont #1}} 

\title{XeLaTeX Multilingual Test Document} 
\author{LaTeX Compiler Workflow}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}

This document tests XeLaTeX compilation with multiple languages and Unicode support. The workflow automatically detected the need for XeLaTeX based on the \texttt{\% !TeX program = xelatex} directive.

\section{European Languages}

\subsection{English}
Hello World! This is a test of the XeLaTeX compiler with modern Unicode fonts.

\subsection{French}
Bonjour le monde! Voici un test avec des caractères accentués: é, è, ê, à, ù, ç, œ.

\subsection{German}
Guten Tag! Test mit deutschen Umlauten: ä, ö, ü, ß.

\subsection{Spanish}
¡Hola mundo! Prueba con caracteres especiales: ñ, á, é, í, ó, ú, ¿, ¡.

\subsection{Portuguese}
Olá mundo! Teste com acentuação: ã, õ, â, ê, ô, à, ç.

\subsection{Italian}
Ciao mondo! Test con caratteri accentati: à, è, é, ì, ò, ù.

\subsection{Russian}
Привет мир! Это тест кириллицы: а, б, в, г, д, е, ё, ж, з, и, й, к.

\subsection{Greek}
Γεια σου κόσμε! Ελληνικά γράμματα: α, β, γ, δ, ε, ζ, η, θ, λ, μ, π, σ, ω.

\section{Middle Eastern Languages}

\subsection{Arabic}
\textarabic{مرحبا بالعالم! هذا اختبار للغة العربية.}

\section{East Asian Languages}

\subsection{Chinese (Simplified)}
\textcjk{你好世界！这是中文测试。汉字：一二三四五六七八九十。}

\subsection{Chinese (Traditional)}
\textcjk{你好世界！這是中文測試。漢字：一二三四五六七八九十。}

\subsection{Japanese}
\textcjk{こんにちは世界！日本語のテストです。ひらがな、カタカナ、漢字。}

\subsection{Korean}
\textcjk{안녕하세요 세계! 한국어 테스트입니다. 한글 문자 테스트.}

\section{Special Characters and Symbols}

\subsection{Mathematical Symbols}
Mathematical symbols work naturally: ∀x ∈ ℝ, ∃y ∈ ℂ, ∞, ∑, ∏, ∫, ∂

Greek letters: α, β, γ, δ, ε, ζ, η, θ, λ, μ, π, σ, τ, φ, χ, ψ, ω

\subsection{Currency Symbols}
Currency symbols: \$, €, £, ¥, ₹, ₽, ₩, ₪

\subsection{Arrows and Operators}
Arrows: →, ←, ↔, ⇒, ⇐, ⇔, ↑, ↓

Operators: ≠, ≤, ≥, ±, ×, ÷, ≈, ≡

\subsection{Geometric and Misc Symbols}
Shapes: ○, ●, □, ■, △, ▲, ◇, ◆

Stars: ★, ☆, ✦, ✧

Punctuation: •, ·, ‣, ⁃

\section{Typography Features}

\subsection{Ligatures}
XeLaTeX handles ligatures automatically: fi, fl, ff, ffi, ffl, fj

The word "office" shows the ffi ligature.

\subsection{Quotation Marks}
Different quotation mark styles:

English: "double quotes" and 'single quotes'

French: « guillemets français »

German: „deutsche Anführungszeichen"

\subsection{Dashes}
Different dash types:

Hyphen: word-word

En-dash: pages 10--20

Em-dash: A sentence---with emphasis

\subsection{Spacing}
Ellipsis: dots... versus proper ellipsis…

Non-breaking space: Mr.~Smith (no line break)

\section{Font Styles}

\subsection{Weight and Style}

\textbf{Bold text} demonstrates font weight.

\textit{Italic text} shows slanted characters.

\textbf{\textit{Bold italic}} combines both styles.

\subsection{Sans Serif}

\textsf{This is sans-serif text using Noto Sans.}

\textsf{\textbf{Bold sans-serif}} and \textsf{\textit{italic sans-serif}}.

\subsection{Monospace}

\texttt{This is monospace text using Noto Sans Mono.}

\texttt{Code example: if (x == 0) \{ return true; \}}

\section{Color Support}

XeLaTeX with xcolor package:

\textcolor{red}{Red text}, \textcolor{blue}{blue text}, \textcolor{green}{green text}.

\textcolor{orange}{Orange}, \textcolor{purple}{purple}, \textcolor{cyan}{cyan}.

Combined: \textcolor{red}{\textbf{bold red text}} and \textcolor{blue}{\textit{italic blue text}}.

\section{Mixed Scripts in One Line}

English, Français, Deutsch, Español all together.

Latin with Greek: The symbol π (pi) represents 3.14159...

Numbers in different scripts: 123 (Western), \textcjk{一二三} (Chinese)

\section{Conclusion}

If this document compiled successfully, it demonstrates:

\begin{enumerate}
    \item \textbf{Compiler Detection:} The workflow detected XeLaTeX from the \texttt{\% !TeX program} directive
    \item \textbf{Font Installation:} Noto fonts were automatically installed
    \item \textbf{Unicode Support:} Full Unicode character rendering works
    \item \textbf{Multilingual:} Latin, Cyrillic, Greek, Arabic, and CJK scripts all render correctly
    \item \textbf{Typography:} Ligatures, proper dashes, and quotation marks function properly
    \item \textbf{OpenType Features:} Modern font features are available
\end{enumerate}

\vspace{1em}

\textbf{Success!} The LaTeX compiler workflow correctly handled:
\begin{itemize}
    \item Multi-document support with smart change detection
    \item Automatic compiler detection (pdflatex/xelatex/lualatex)
    \item On-demand installation of compilers and fonts
    \item Efficient caching for subsequent runs
\end{itemize}

This test document validates that the workflow is production-ready for complex multilingual documents.

\end{document}
