

\mychapter{0}{Dedication}

To my parents, who raised me right. You have always been my source of energy. You taught me how to be a good person, and how our lives do not matter if we do not leave an impact on the people around us. The love you hold for each other and your children has been my biggest inspiration.
I hope that one day, I can be lucky enough to repay you for all your sacrifices and be the essence of your well-being and happiness. 
\vspace*{0.4cm}

To my sister and my Hero, Nada; I look up to you every single day. You were there for me each time my world was torn to pieces, and when I felt like I was on top of it, you were the first person that I wanted to share the feeling with. To say that your beautiful soul has made me a better person is an understatement. I am proud to have known you in this life, and I know that if we meet in the next one, you will undoubtedly be my hero.
\vspace*{0.15cm}

To my brother Sami; I admire the way you live your life. You are full of hope, dreams, and the determination to make them true. Your dedication to the people you care for is very moving. You taught me that life can still be fun no matter the impediments I face. You are growing up so quickly. I am very proud of the amazing person you are becoming.
\vspace*{0.15cm}

To my friends, Imane, Boutayna, Maha, and Mohamed, I would like to thank you for the moments we shared, the ups that strengthened our bond, and the downs that made us believe that family is far from being related to blood. It is with you that I learned what friendship means. I am so grateful to God for the opportunity to have known such beautiful hearts. 
\vspace*{0.4cm}

To my grandparents, to my aunts and uncles, to my cousins, I am thankful for our big family, for your support, and for witnessing what prioritizing the people you love really is.
\vspace*{0.4cm}

To my pets, thank you for teaching me innocence, bravery, and that life is more than trying to fit in. My love for you holds so much courage in it. 

\bigskip
\medskip
\begin{center}
\large{
\textit{\uppercase{T}o you all, I dedicate this humble work. \\[5pt]}
}

\end{center}
\
\medskip



\clearpage